Double White Dwarf Mergers with CASTRO\\ I. Methodology and Code Verification

### 2014-08-04 paper.tex
Got started on the introduction.

>>>>

Type Ia supernovae (SNe Ia) are currently some of the most exciting events to study in astrophysics. These bright, brief pulses of light in the distant universe have led to a number of important discoveries in recent years, including the discovery of the accelerated expansion of the universe \citep{perlmutter1999,riess1998}. However, their origin is shrouded in mystery. It has long been expected that these events arise from the thermonuclear explosions of white dwarfs \citep{hoyle_fowler:1960}, but the cause of these explosions is uncertain. In particular, it is not clear what process causes the temperatures in these white dwarfs to become hot enough for explosive burning of its constituent nuclei. The model favored initially by the community was the so-called single-degenerate (SD) model. Accretion of material from a companion star such as a red giant would cause the star to approach the Chandrasekhar mass, and in doing so the temperature and density in the center would become sufficient for thermonuclear fusion to proceed. A review of the observational evidence and theoretical modelling that formed this belief can be found in \citet{hillebrandtniemeyer2000}.
